What We Eval in the Shadows

### 2021-08-09 paper/main.tex
Formatting changes in 3.1

We distinguish three sources for calls to \eval, those originating from
\emph{Base} libraries bundled with R, packages hosted on \emph{CRAN}, and
end-user scripts from \emph{Kaggle}. We consider base libraries as part of the
language implementation and do not include them in our analysis.

\mypara{Base.} The \BasePackages base libraries provide arithmetics, statistics,
and operating system functionalities. Base has \BaseFunsWithEvals functions with
\BaseEvalCallSites calls to \eval. These functions perform key tasks such as
package loading, there is thus hardly any R program that does not invoke them.

\mypara{CRAN.} Packages hosted on the Comprehensive R Archive Network ({\small
\url{cran.r-project.org}}, aka CRAN) have three sources of runnable: unit
\emph{tests} for individual functions, code \emph{examples} embedded in the
documentation, and use-cases called \emph{vignettes}. All runnable snippets
can be extracted into independent files. We download \CranPackages packages and
extract \CranRunnableScripts scripts with \CranRunnableCode lines of code
(\CranRunnableCodeExamplesRnd in examples, \CranRunnableCodeVignettesRnd in
vignettes and \CranRunnableCodeTestsRnd in tests). CRAN packages contain 20
years of contribution from thousands from thousands of authors, often
experienced R developers.

\mypara{Kaggle.} Kaggle ({\small \url{kaggle.com}}) is an online platform that
allows users to submit and compete to solve problems. We download \KaggleUnique
unique scripts and notebooks with their input files (\KaggleDuplicates
duplicates were removed using SHA-1 hashes); 665K lines of R code making only
\KaggleWithEvals calls \eval. Authors of these scripts have highly variable
levels of expertise.

@@

\begin{enumerate}
\item \emph{Download.} Packages are downloaded from CRAN, for Kaggle a web
  crawler retrieves code, and a command-line tool gets data. Installation is
  complicated by native dependencies which sometimes have to be resolved
  manually.
\item \emph{Extract.} The \genthat tool extracts all runnable code snippets and
  turns each of these into a self-standing program~\cite{issta18}, \c{knitr}
  extracts code from notebooks. Each extracted script is instrumented with calls
  to our dynamic analyzer in a way that avoid recording calls to \eval
  originating from our execution harness.
\item \emph{Trace.} Script run with a modified R interpreter to capture
  execution traces. Each script is run in its own process with the GNU R
  compiler turned off to avoid recording its execution. CRAN scripts run twice,
  once to capture \eval calls originating from package code and a second time to
  capture calls coming from base libraries.
\item \emph{Analyze.} Analysis outputs are merged, cleaned, and summarized.
  RMarkdown notebooks process the summarized data to generate all graphs (PDF
  from \c{ggplot2}) and numbers (exported as \LaTeX macros) appearing in the
  paper.
\end{enumerate}

>>>>

We distinguish three sources for calls to \eval, those originating from
\emph{Base} libraries bundled with R, packages hosted on \emph{CRAN}, and
end-user scripts from \emph{Kaggle}:

\begin{itemize}[$-$]

\item \emph{Base.} The \BasePackages base libraries provide arithmetics,
  statistics, and operating system functionalities. Base has \BaseFunsWithEvals
  functions with \BaseEvalCallSites calls to \eval. These functions perform key
  tasks such as package loading, there is thus hardly any R program that does
  not invoke them. We consider base libraries as part of the language
  implementation and do not include them in our analysis.

\item \emph{CRAN.} Packages hosted on the Comprehensive R Archive Network
  ({\small \url{cran.r-project.org}}, aka CRAN) have three sources of runnable:
  unit \emph{tests} for individual functions, code \emph{examples} embedded in
  the documentation, and use-cases called \emph{vignettes}. All runnable
  snippets can be extracted into independent files. We download \CranPackages
  packages and extract \CranRunnableScripts scripts with \CranRunnableCode
  lines of code (\CranRunnableCodeExamplesRnd in examples,
  \CranRunnableCodeVignettesRnd in vignettes and \CranRunnableCodeTestsRnd in
  tests). CRAN packages contain 20 years of contribution from thousands from
  thousands of authors, often experienced R developers.

\item \emph{Kaggle.} Kaggle ({\small \url{kaggle.com}}) is an online platform
  that allows users to submit and compete to solve problems. We download
  \KaggleUnique unique scripts and notebooks with their input files
  (\KaggleDuplicates duplicates were removed using SHA-1 hashes); 665K lines of
  R code making only \KaggleWithEvals calls \eval. Authors of these scripts
  have highly variable levels of expertise.

\end{itemize}

@@

\begin{compactenum}[(1)]
\item \emph{Download.} Packages are downloaded from CRAN, for Kaggle a web
  crawler retrieves code, and a command-line tool gets data. Installation is
  complicated by native dependencies which sometimes have to be resolved
  manually.
\item \emph{Extract.} The \genthat tool extracts all runnable code snippets and
  turns each of these into a self-standing program~\cite{issta18}, \c{knitr}
  extracts code from notebooks. Each extracted script is instrumented with calls
  to our dynamic analyzer in a way that avoid recording calls to \eval
  originating from our execution harness.
\item \emph{Trace.} Script run with a modified R interpreter to capture
  execution traces. Each script is run in its own process with the GNU R
  compiler turned off to avoid recording its execution. CRAN scripts run twice,
  once to capture \eval calls originating from package code and a second time to
  capture calls coming from base libraries.
\item \emph{Analyze.} Analysis outputs are merged, cleaned, and summarized.
  RMarkdown notebooks process the summarized data to generate all graphs (PDF
  from \c{ggplot2}) and numbers (exported as \LaTeX macros) appearing in the
  paper.
\end{compactenum}
